---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# defender

[![Travis build status](https://travis-ci.org/ropenscilabs/defender.svg?branch=master)](https://travis-ci.org/ropenscilabs/defender)
[![Coverage status](https://img.shields.io/codecov/c/github/ropenscilabs/defender/master.svg)](https://codecov.io/github/ropenscilabs/defender?branch=master)

The goal of defender is to do static code analysis on other R packages to check for potential security risks and best practices. It provides checks on multiple levels:

1. [x] static code analysis without installing the package
2. [ ] more thorough but potentially dangerous checks with installation / in Docker container

## Installation

You can install defender from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ropenscilabs/defender")
```

## Example

You can check for system calls in any directory locally available:

```{r example}
summarize_system_calls("./testevil")
```
